Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-07-03 doc/RMD/pop-diff.Rmd
add poppr table to manuscript

@@

```{r dapc-region, fig.width = 7, fig.height = 7}
region.dapc <- dapc(dat11, strata(dat11)$Region, n.pca = 25, n.da = 14)
scatter(region.dapc)
ggcompoplot(region.dapc, setPop(dat11, ~Region), pal = funky, cols = 2)
```

>>>>

# Genotypic Diversity

```{r geno-div, cache = TRUE, fig.width = 10, fig.height = 10, comment = NA}
ptab <- dat11cc %>% setPop(~Region) %>% poppr(sample = 999, total = FALSE)
```

```{r geno-div2, fig.width = 10, fig.height = 10, comment = NA}
ptab %>%
  arrange(desc(N), desc(MLG)) %>%
  mutate(Ia = case_when(
    !is.finite(.$p.Ia) ~ "-",
    .$p.Ia == 0.001 ~ paste0(round(.$Ia, 2), "*"),
    .$p.Ia <= 0.01 ~  paste0(round(.$Ia, 2), "-"),
    .$p.Ia <= 0.05 ~  paste0(round(.$Ia, 2), "~"),
    TRUE ~ as.character(round(.$Ia, 2))
  )) %>%
  mutate(rbarD = case_when(
    !is.finite(.$p.rD) ~ "-",
    .$p.rD == 0.001 ~ paste0(round(.$rbarD, 2), "*"),
    .$p.rD <= 0.01 ~  paste0(round(.$rbarD, 2), "-"),
    .$p.rD <= 0.05 ~  paste0(round(.$rbarD, 2), "~"),
    TRUE ~ as.character(round(.$rbarD, 2))
  )) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  mutate(N = paste(N, MLG, sep = " (") %>% paste0(")") %>% formatC()) %>%
  mutate(eMLG = paste(eMLG, SE, sep = " (") %>%  paste0(")") %>% formatC()) %>%
  rename(`*h*` = Hexp) %>%
  rename(`$E_5$` = E.5) %>%
  rename(`$I_A$` = Ia) %>%
  rename(`$\\lambda$` = lambda) %>%
  rename(`$\\bar{r}_d$` = rbarD) %>%
  select(-File, -MLG, -SE, -p.rD, -p.Ia) %>% 
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 4:5, 1) %>%
  huxtable::set_align(huxtable::everywhere, -1, "right") %>%
  huxtable::set_col_width(c(1.1, 0.9, 1.3, 0.5, 0.5, 1.2, 0.7, 0.6, 0.6, 0.8)) %>%
  huxtable::print_md(max_width = 80)

ptab %>% 
  arrange(desc(N), desc(MLG)) %>% 
  write_csv(file.path(PROJHOME, "results/tables/genotype_diversity_table_region.csv"), col_names = TRUE)

mtab <- mlg.table(dat11, ~Region, background = TRUE)
```

@@

```{r dapc-region, fig.width = 7, fig.height = 7}
region.dapc <- dapc(dat11, strata(dat11)$Region, n.pca = 25, n.da = 14)
scatter(region.dapc, scree.pca = TRUE,
        bg = "grey80",
        col = funky(nlevels(strata(dat11)$Region)), 
        posi.pca = "topright"
        )
ggcompoplot(region.dapc, setPop(dat11, ~Region), pal = funky, cols = 2)
```

### 2017-07-03 doc/manuscript/manuscript.Rmd
add poppr table to manuscript

>>>>

----------------------------------------------------------------------------
Pop             N        eMLG    H    G  $\lambda$  $E_5$   *h* $I_A$ $\bar{ 
                                                                       r}_d$ 
--------- ------- ----------- ---- ---- ---------- ------ ----- ----- ------
WA        58 (56) 9.95 (0.23)  4.0 54.3       0.98   0.98  0.60 0.65*  0.07*

MI        58 (43)  9.3 (0.79)  3.6 29.0       0.97   0.78  0.54 1.25*  0.14*

ND        41 (35) 9.44 (0.73)  3.5 25.9       0.96   0.82  0.54    1*   0.1*

NE        37 (28) 8.93 (0.94)  3.2 17.8       0.94   0.75  0.55 2.22*  0.25*

CO        34 (28) 9.46 (0.67)  3.3 24.1       0.96   0.92  0.56 2.33*  0.27*

France    21 (14)  8.5 (0.85)  2.6 12.6       0.92   0.95  0.48 0.94*  0.11*

CA        18 (15) 9.12 (0.72)  2.7 13.5       0.93   0.94  0.51 0.28~  0.03~

OR        17 (13) 8.52 (0.85)  2.5 10.7       0.91   0.89  0.47 0.92*   0.1*

Mexico     15 (9)  7.1 (0.85)  2.1  7.3       0.86   0.89  0.28 2.57*  0.37*

MN          9 (7)       7 (0)  1.9  6.2       0.84   0.93  0.47 1.34*  0.19*

Australia   6 (6)       6 (0)  1.8  6.0       0.83   1.00  0.48  0.7~  0.12~

WI          2 (2)       2 (0)  0.7  2.0       0.50   1.00  0.27     -      -

NY          1 (1)       1 (0)  0.0  1.0       0.00    NaN   NaN     -      -

ID          1 (1)       1 (0)  0.0  1.0       0.00    NaN   NaN     -      -

----------------------------------------------------------------------------

Table: (\#tab:iatab) Genotypic diversity and Linkage Disequilibrium summary for geographic populations arranged by abundance after clone-correction by a hierarchy of Region/Source/Host/Year. 
Pop = Population, N = number of individuals (number of MLG in parentheses), 
eMLG = expected number of MLGs based on rarefaction at 10 individuals (standard error in parentheses), 
H = Shannon-Weiner Index, G = Stoddardt and Taylor's Index, 
$\lambda$ = Simpson's Index, 
*h* = Nei's 1978 gene diversity, 
$I_A$ = the index of association, 
$\bar{r}_d$ = standardized index of association. 
P-value symbols: \* = 0.001, ~ = $\leq 0.05$.
